\documentclass{article}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\usepackage[margin=1in]{geometry}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{listings}
\input{PDDL}

\begin{document}
\today

\section*{Problem Formulation}
The metalevel search space:
The MDP $<S, A, T, R, s, t>$
\begin{itemize}
\item A set of states $s \in S$. 
\item A set of actions $a \in A$.
\item A transition function $T(s,a,s')$.
\item A reward function $R(s)$.
\item A start state $s$.
\item A terminal state $t$.
\end{itemize}

The state: A state $s$ is an object model consists of a grounded PDDL domain model $<P, A>$. 
\begin{itemize} 
\item A set of propositions $P$.
\item A set of actions $a^{PRE}_{EFF} \in A$.
\item Each action $a^p_e$ has a set $PRE$ of preconditions and a set $EFF$ of effects. 
\end{itemize}


Working Domain:
\begin{lstlisting}[caption={LightSwitch Domain},
  label={lst:pddlmove},
  language=PDDL]
:predicates(
	(switch1_on)
	(lightbulb_on)
)

(:action switchon_sw1
	:parameters ()
	:precondition (and (not (switch1_on)))
	:effect (and (switch1_on) (lightbulb_on))
)

(:action switchoff_sw1
	:parameters ()
	:precondition (and (switch1_on))
	:effect(and (not (switch1_on)) (not (lightbulb_on))
)
\end{lstlisting}

\pagebreak
\section*{State Metaspace Analysis}
Let $p$ be the number of predicates, $a$ be the number of actions. 

Each action has a set $PRE$ and $EFF$ of propositions. For each proposition, there are three possible values that it can take on in a concrete instance of the model:
\begin{itemize}
\item The proposition can belong to clause as a positive literal.
\item The proposition can belong to a clause as a negative literal.
\item The proposition can not belong to the clause. 
\end{itemize}
Thus, for each action, there are $3^{2p}$ possibilities. For all $a$ actions, there are $\prod_1^a 3^{2p} = (3^{2p})^a = 3^{2ap}$ possibilities.

For the example domain,we have $p=2$ predicates and $a=2$ actions and $3^{2ap} = 3^{2*2*2} = 3^8 = 6561$ possible domain models.

\section*{Action Metaspace Analysis}
Let $p$ be the number of predicates, $a$ be the number of actions. Given a metastate $s$ in the metaspace $S$, each proposition can be changed to one of the other two possibile values. Thus, there are $4ap$ metaactions.
\end{document} 
